Flatiron cleaning

### 2021-10-21 Rmd/rdi analysis.Rmd
Add continous analysis

## Univariable
```{r Table 5 HR}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- tbl1 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl2 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl3 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Cisplatin
tbl4 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- tbl4 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl4$month_at_os_from_treatment, event = tbl4$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl5 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl5 <- tbl5 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl5$month_at_os_from_treatment, event = tbl5$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

tbl6 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl6 <- tbl6 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl6$month_at_os_from_treatment, event = tbl6$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl4, tbl5, tbl6),
          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Pacli
tbl7 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
tbl7 <- tbl7 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl8 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl8 <- tbl8 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl9 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl9 <- tbl9 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl_stack(list(tbl7, tbl8, tbl9),
          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# PPB
tbl10 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl10$month_at_os_from_treatment, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl11 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl11 <- tbl11 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl11$month_at_os_from_treatment, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl12 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl12 <- tbl12 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl12$month_at_os_from_treatment, event = tbl12$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl10, tbl11, tbl12),
          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# docetaxel
tbl13 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
tbl13 <- tbl13 %>%
  select(vitalstatus, RDI_grp) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl13$month_at_os_from_treatment, event = tbl13$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl14 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl14 <- tbl14 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl14$month_at_os_from_treatment, event = tbl14$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl15 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl15 <- tbl15 %>%
  select(vitalstatus, RDI_grp) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl15$month_at_os_from_treatment, event = tbl15$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

tbl_stack(list(tbl13, tbl14, tbl15),
          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()
```

## Multivariable
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- 
  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

@@

### Multivariable
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
```{r}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- 
  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
             event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

@@

# docetaxel
tbl13 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
tbl13 <- 
  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
             event = tbl13$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl13) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl14 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl14 <- 
  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
             event = tbl14$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl14) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl15 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl15 <- 
  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
             event = tbl15$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl15) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl13, tbl14, tbl15),
          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()
```

@@

# VI. Adjusted by BMI

>>>>

## Univariable
```{r Table 5 HR}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- tbl1 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl2 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl3 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin/Neoadjuvant", "carboplatin/Adjuvant Upfront Surgery", "carboplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Cisplatin
tbl4 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Neoadjuvant")
tbl4 <- tbl4 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl4$month_at_os_from_treatment, event = tbl4$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl5 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl5 <- tbl5 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl5$month_at_os_from_treatment, event = tbl5$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

tbl6 <- Frontline %>%
  filter(str_detect(drugname,"cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl6 <- tbl6 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl6$month_at_os_from_treatment, event = tbl6$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl4, tbl5, tbl6),
          group_header = c("cisplatin/Neoadjuvant", "cisplatin/Adjuvant Upfront Surgery", "cisplatin/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# Pacli
tbl7 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant")
tbl7 <- tbl7 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl8 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl8 <- tbl8 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl9 <- Frontline %>%
  filter(drugname =="paclitaxel" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl9 <- tbl9 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
tbl_stack(list(tbl7, tbl8, tbl9),
          group_header = c("paclitaxel/Neoadjuvant", "paclitaxel/Adjuvant Upfront Surgery", "paclitaxel/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# PPB
tbl10 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl10$month_at_os_from_treatment, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl11 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl11 <- tbl11 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl11$month_at_os_from_treatment, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl12 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl12 <- tbl12 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl12$month_at_os_from_treatment, event = tbl12$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl10, tbl11, tbl12),
          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant Upfront Surgery", "PPB/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()

# docetaxel
tbl13 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
tbl13 <- tbl13 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl13$month_at_os_from_treatment, event = tbl13$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl14 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl14 <- tbl14 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl14$month_at_os_from_treatment, event = tbl14$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl15 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl15 <- tbl15 %>%
  select(vitalstatus, RDI_grp, mean_RDI_per_drug) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl15$month_at_os_from_treatment, event = tbl15$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

tbl_stack(list(tbl13, tbl14, tbl15),
          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

## Multivariable
### RDI group
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~RDI_grp + raceeth + ageatdx + stagecat` 
```{r Table 5 HR adjusted rdi group}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- 
  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
             event = tbl1$vitalstatus) ~ RDI_grp + raceeth + ageatdx + stagecat, data =  tbl1) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

@@

### Multivariable
`coxph(Surv(time = month_at_os_from_treatment, event = vitalstatus)~ RDI_grp + raceeth + ageatdx + stagecat` 
```{r}
# Carbo
tbl1 <- Frontline %>%
  filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant")
tbl1 <- 
  coxph(Surv(time = tbl1$month_at_os_from_treatment, 
             event = tbl1$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl1) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")

@@

# docetaxel
tbl13 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Neoadjuvant")
tbl13 <- 
  coxph(Surv(time = tbl13$month_at_os_from_treatment, 
             event = tbl13$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl13) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl14 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery")
tbl14 <- 
  coxph(Surv(time = tbl14$month_at_os_from_treatment, 
             event = tbl14$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl14) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl15 <- Frontline %>%
  filter(str_detect(drugname, "docetaxel") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo")
tbl15 <- 
  coxph(Surv(time = tbl15$month_at_os_from_treatment, 
             event = tbl15$vitalstatus) ~ RDI_grp1 + raceeth + ageatdx + stagecat, data =  tbl15) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level")
tbl_stack(list(tbl13, tbl14, tbl15),
          group_header = c("docetaxel/Neoadjuvant", "docetaxel/Adjuvant Upfront Surgery", "docetaxel/Adjuvant Upfront Chemo")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

@@

# VI. Adjusted by **BMI at DX category**
